A Hierarchical Bayesian Framework for Inferring the Stellar Obliquity Distribution

### 2023-05-01 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[twocolumn,times]{aastex631}
\usepackage{showyourwork}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{physics}
\usepackage[super]{nth}
\usepackage{fontawesome}
\usepackage{hyperref}

@@

When applying the framework to all exoplanetary systems with measured sky-projected stellar obliquity, which are mostly Hot Jupiter systems, we find that the inferred population-level obliquity distribution is unimodal and peaked at zero degrees. The misaligned systems have nearly isotropic stellar obliquities with no strong clustering near 90$\degr$.
The diverse range of stellar obliquities prefers dynamic mechanisms, such as planet-planet scattering after a convergent disk migration, which could produce both prograde and retrograde orbits with no strong inclination concentrations.

>>>>

% Define document class
\documentclass[twocolumn,times,linenumbers]{aastex631}
\usepackage{showyourwork}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{physics}
\usepackage[super]{nth}
\usepackage{fontawesome}
\usepackage{hyperref}

@@

When applying the framework to all systems with measured sky-projected stellar obliquity, which are mostly Hot Jupiter systems, we find that the inferred population-level obliquity distribution is unimodal and peaked at zero degrees. The misaligned systems have nearly isotropic stellar obliquities with no strong clustering near 90$\degr$.
The diverse range of stellar obliquities prefers dynamic mechanisms, such as planet-planet scattering after a convergent disk migration, which could produce both prograde and retrograde orbits with no strong inclination concentrations of close-in planets.
